---
title: "Oil Palm Growers MY"
author: "LiyanaZulkipli"
knit: (function(input_file, encoding) {
    out_dir <- 'docs1';
    rmarkdown::render(input_file,
      encoding=encoding,
      output_file=file.path(dirname(input_file), out_dir, 'MSPO_Certification_Code.html'))})
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#MSPO Certification

The dataset sourced for the demographic of oil palm growers in Malaysia is taken from [MSPO Trace](https://mspotrace.org.my/Opmc_list). The MSPO Trace is a complete solution to track and trace MSPO Certification, from oil palm plantings and down to the supply chain.

##MS 2530-3:2013 / MSPO Part 3 (2013 version)

**General Principles for Oil Palm Plantations** Part 3 contains requirements used to assess conformity for oil palm estates or plots against the MSPO. This sheet will demonstrate the oil palm plantation that is certified against Part 3 of MSPO standard. 

```{r message=FALSE}
library(readxl)
library(writexl)
list1 <- read_excel("list1.xlsx")
print("Fields in the MSPO Trace Dataset")
colnames(list1)
```

A glimpse of the columns in the dataset shows the information monitored by the MPOCC including the state and certified area. A further inspection of the dataset found that the Part 3 Certification is a compilation of small plots to big estates. 

The recently developed MSPO standard (2022) has redefined the certification based on the size of certified oil palm area namely:

* MS2530-2-2:2022 - MSPO Part 2-2: General Principles for Organised Smallholders (less than 40.46 hectares). 
* MS2530-3-1:2022 - MSPO Part 3-1: General Principles for Oil Palm Plantations (40.46 hectares to 500 hectares)
* MS2530-3-2:2022 - MSPO Part 3-2: General Principles for Oil Palm Plantations (more than 500 hectares). 

The total certified area is calculated for every plot and estate certified with 2013 MSPO Part 3 Certification in each state.

```{r message=FALSE}
library(dplyr)

#filter only Part 3 Certificate with selected columns
Part3 <- list1 %>% 
  filter(Certification == "Part 3") %>% 
  select(Certification, `Certified Entity / Cluster`, `Certified Area (Ha)`, State)

#rename column names
colnames(Part3)[2] = 'Entity'
colnames(Part3)[3] = 'Area'

```


```{r message =FALSE}

library(knitr)
Part3_CertifiedArea <- Part3 %>%
  group_by(State) %>%
  summarise(Total_Area = sum(Area)) %>%
  arrange(desc(Total_Area))

kable(Part3_CertifiedArea, caption = 'Total Certified Area for 2013 MSPO Part 3 Certification', "simple")
```


Characterising the certification into the size of certified area based on the 2022 MSPO standard. 

```{r message=FALSE}
Part3_Type <- Part3 %>%
  mutate(Type = case_when(Area <= 40.46 ~ 'Smallholders with below 40.46 Ha plot - MS2530-2-2',
                          Area > 40.46 & Area <= 500 ~ 'Growers with 40.46 to 500 Ha estate - MS2530-3-1',
                          Area > 500 ~ 'Growers with above 500 Ha estate - MS2530-3-2'))
```

The total certified area for each type of growers can be shown in the dataframe below.
```{r message=FALSE}
Type_State_CertifiedArea <- Part3_Type %>%
  group_by(Type, State) %>%
  summarise(Total_Area = sum(Area))
```

```{r message=FALSE}
kable(Type_State_CertifiedArea, caption = 'Total Certified Area based on the 2022 MSPO standard')
```

Part 2 Certification for the MSPO 2022 version is only eligible for Smallholder with plantation size of below 40.46 ha. 

```{r message=FALSE}
Part2_CertifiedArea <- Part3_Type %>%
  group_by(Type) %>%
  summarise(Total_Area = sum(round(Area, 3)))

cat("Total Certified Area for Part 2 Certification is ", round(Part2_CertifiedArea$Total_Area[3])," Ha")

```

Let's identify the total certified area for Part 3 certification in Malaysia.
 
```{r message=FALSE}
Part3_2022 <- Part3_Type %>%
  group_by(Type) %>%
  filter(Type != "Smallholders with below 40.46 Ha plot - MS2530-2-2") %>%
  summarise(Total_Area = sum(round(Area, 3)))

Certification <- Part3_2022$Type
kable(Part3_2022, caption = 'Total Certified Area for 2022 MSPO Part 3 Certification')
```
